Tropical Andes Functional diversity for plants and Frugivores

### 2023-10-18 code/L2/L2_1_TropicalAndes_funcdiv.Rmd
update forest subset file type -> switch to sf

# Read in Data
```{r}
TropicalAndes_plant_occ_forest <- read.csv(file.path(data_path,"TropicalAndes_plant_occ_forest.csv"))
TropicalAndes_frugivore_occ_forest <- read.csv(file.path(data_path,"TropicalAndes_frugivore_occ_forest.csv"))
TropicalAndes_IUCNHabitat_Forest <- raster(file.path(data_path2, "TropicalAndes_IUCNHabitat_Forest.tif"))
frugivore_traits <- read.csv(file.path(data_path,"TropicalAndes_Frugivoria_traits_Forest.csv"))
plant_traits <- read.csv(file.path(data_path,"TropicalAndes_plant_traits_forest.csv"))
```

@@

```{r}
coordinates_sf_plant <- st_as_sf(TropicalAndes_plant_occ_forest_sub, coords = c("decimalLongitude", "decimalLatitude"), crs = st_crs(Forest_sf))
coordinates_sf_frugivore <- st_as_sf(TropicalAndes_frugivore_occ_forest_sub, coords = c("decimalLongitude", "decimalLatitude"), crs = st_crs(Forest_sf))
```

```{r}
# Perform the spatial intersection
intersections_plant_TA <- st_intersection(coordinates_sf_plant, Forest_sf)
intersections_frugivore_TA <- st_intersection(coordinates_sf_frugivore, Forest_sf)
# Convert the intersected sf object back to a dataframe
coordinates_df_subset_plant <- as.data.frame(intersections_plant_TA)
coordinates_df_subset_frugivore <- as.data.frame(intersections_frugivore_TA)
```

@@

# Assign row names to the matrix
rownames(plant_traits_matrix) <- row_names_plant
rownames(frugivore_traits_matrix) <- row_names_frugivore
# Turn back into dataframe
plant_traits_df_final <-as.data.frame(plant_traits_matrix)
frugivore_traits_df_final <-as.data.frame(frugivore_traits_matrix)
plant_traits_df$X <-NULL
frugivore_traits_df$X <-NULL
```

>>>>

# Read in Data
```{r}
TropicalAndes_plant_occ_forest <- read.csv(file.path(data_path,"TropicalAndes_plant_occ_forest.csv"))
TropicalAndes_frugivore_occ_forest <- read.csv(file.path(data_path,"TropicalAndes_frugivore_occ_forest.csv"))
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path2, "Forest_sf.shp"), layer = "Forest_sf")
frugivore_traits <- read.csv(file.path(data_path,"TropicalAndes_Frugivoria_traits_Forest.csv"))
plant_traits <- read.csv(file.path(data_path,"TropicalAndes_plant_traits_forest.csv"))
```

@@

```{r}
coordinates_sf_plant <- st_as_sf(TropicalAndes_plant_occ_forest, coords = c("decimalLongitude", "decimalLatitude"), crs = st_crs(TropicalAndes_IUCNHabitat_Forest))
coordinates_sf_frugivore <- st_as_sf(TropicalAndes_frugivore_occ_forest, coords = c("decimalLongitude", "decimalLatitude"), crs = st_crs(TropicalAndes_IUCNHabitat_Forest))
```

```{r}
# Perform the spatial intersection
intersections_plant_TA <- st_intersection(coordinates_sf_plant, TropicalAndes_IUCNHabitat_Forest)
intersections_frugivore_TA <- st_intersection(coordinates_sf_frugivore, TropicalAndes_IUCNHabitat_Forest)
# Convert the intersected sf object back to a dataframe
coordinates_df_subset_plant <- as.data.frame(intersections_plant_TA)
coordinates_df_subset_frugivore <- as.data.frame(intersections_frugivore_TA)
```

@@

# Assign row names to the matrix
rownames(plant_traits_matrix) <- row_names_plant
rownames(frugivore_traits_matrix) <- row_names_frugivore
# Turn back into dataframe
plant_traits_df_final <-as.data.frame(plant_traits_matrix)
frugivore_traits_df_final <-as.data.frame(frugivore_traits_matrix)
plant_traits_df_final$X <-NULL
frugivore_traits_df_final$X <-NULL
```
